Dynamic Knapsack Problem

### 2021-05-18 Manuscript/Manuscript.tex
fixed a few mistakes with simulation
- Added ability for resources to be carried over
- Changed how action is generated to be correct (exclude current state value)

TODO:
- fas simulation

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
\end{equation}
Subject to:
\begin{equation}\begin{alignedat}{10}
\label{full-adp-equation}
	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
		\beta^0 + \\
	& 	\bigg( \sum_{p} \beta_{1p}^{ue} 
			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{d} \bigg) + \\
	& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
			( \hat{uu}_{t+1,p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})) \bigg) +
		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
	\Bigg) \ge v(\vec{ue}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{alignedat} \end{equation}
\begin{equation}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation}
And all auxiliary constraints in "\nameref{auxiliary constraints}"

@@

\subsection{Generating an Action}
Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
\begin{equation*}
	\min_{\vec{A}} c(\vec{S}, \vec{A}) - \gamma v(S')
\end{equation*}	
\begin{align*}
	v(S') = \bigg(  & \beta^0 + \sum_{t=2p}^{T} \beta_{tp}^{ue} uen_{p} + \\ 
	& \sum_{p} \beta_{1p}^{ue} \Big( uen_{p} + ue_{1p} - uu_{1p} - 
		\sum_{dc} U_{pdc} (\sum_{m} sc_{1mdc} + \sum_{t'm} rsc_{1t'mdc} - \sum_{tm} rsc_{t1mdc}) \Big) + \\
	& \sum_{tp}^{T-1} \beta_{tp}^{uu} \Big( uu_{t+1p} + 
		\sum_{mdc} ps_{tmdc}pwp_{} (U_{pd+1c} - U_{pdc}) + 
		U_{pdc} \big( \sum_{mdc} sc_{t+1}  - \sum_{t'mdc} rsc_{t+1t'} + 
		\sum_{tmdc} rsc_{tt'+1} \big) \Big) + \\
	& \sum_{dc} \beta_{0dc}^{pw} E[pea_{dc}]) + \\
	& \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} \Big( pw_{m-1dc} (1 - pwp) + pw_{m-1d-1c} pwp - \sum_{t} sc_{tm-1dc} \Big) + \\
	& \sum_{dc} \beta_{Mdc}^{pw} \sum_{M-1}^{M} \Big( pw_{mdc} (1 - pwp) + pw_{md-1c} pwp - \sum_{t} sc_{tmdc} \Big) + \\
	& \sum _{t=1 m=1 dc}^{T-1 M-1} \beta_{tmdc}^{ps} 
		\Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} - \\
		& - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) + \\
	& \sum _{t=1dc}^{T-1} \beta_{tMdc}^{ps} \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
	&  - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg)
	& \bigg)
\end{align*}
Subject to:
constraints in section "\nameref{state-action constraints}"

>>>>

This gives the following LP
\begin{equation}
	\max_{\vec{\beta}} \sum \alpha (\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps}) v(\vec{ue}, \vec{uu}, \vec{pw}, \vec{pe}, \vec{ps})
\end{equation}
Subject to:
\begin{equation}\begin{alignedat}{10}
\label{full-adp-equation}
	& c(\vec{\hat{pw}}, \vec{\hat{ps}}, \vec{rsc}, \vec{uv}) + \gamma \sum_{\vec{p}} p \Bigg( 
		\beta^0 + \\
	& 	\bigg( \sum_{p} \beta_{1p}^{ue} 
			(ue_{2p} + ued_{p} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
		\bigg( \sum_{t=2,p}^{T-1} \beta_{tp}^{ue} ue_{t+1,p} \bigg)+ 
		\bigg( \sum_{p} \beta_{Tp}^{ue} uen_{p} \bigg) + \\
	& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
			( \hat{uu}_{t+1,p} + \sum_{mdc} pst_{tmdc} (U_{pd+1c} - U_{pdc})) \bigg) +
		\bigg( \sum_{p} \beta_{Tp}^{uu} * 0 \bigg) + \\
	& 	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
		\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
			(\hat{pw}_{m-1dc} + pwt_{m-1d-1c} - pwt_{m-1dc}) \bigg) + \\
	&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
			(\sum_{M-1}^{M} \hat{pw}_{mdc} + pwt_{md-1c} - pwt_{mdc})\bigg) + \\
	& 	\bigg( \sum_{tdc} \beta_{t0dc}^{ps} 0 \bigg) +
		\bigg( \sum_{mdc} \beta_{Tmdc}^{ps} 0 \bigg) +
		\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
			(\hat{ps}_{t+1m-1dc} + pst_{t+1m-1d-1c} - pst_{t+1m-1dc}) \bigg) + \\	
	&	\bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
			(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + pst_{t+1md-1c} - pst_{t+1mdc})) \bigg)
	\Bigg) \ge v(\vec{ue}, \vec{pw}, \vec{ps}) \quad \forall \vec{S} \vec{A}
\end{alignedat} \end{equation}
\begin{equation}
	\vec{\beta} \ge 0 \quad \forall \beta
\end{equation}
And all auxiliary constraints in "\nameref{auxiliary constraints}"

@@

\subsection{Generating an Action}
Once $\vec{\beta}$ values have been approximated, you may use the model below to generate a recommended action for a specific state.
\begin{equation*}
	\min_{\vec{A}} c(\vec{S}, \vec{A}) - \gamma v(S')
\end{equation*}

\begin{equation}\begin{alignedat}{10}
	&	v(S') = \Bigg( 
		&& 	\beta^0 + 
			\bigg( \sum_{p} \beta_{1p}^{ue} 
				(uen_{d} + ue_{1p} - \hat{uu}_{1p}) \bigg)+
			\bigg( \sum_{t=2,p}^{T} \beta_{tp}^{ue} uen_{d} \bigg)+ \\
	&	&& 	\bigg( \sum_{tp}^{T-1} \beta_{tp}^{uu} 
				( \hat{uu}_{t+1,p} + \sum_{mdc} E[pst_{tmdc}] (U_{pd+1c} - U_{pdc})) \bigg) + \\
	&	&&	\bigg( \sum_{dc} \beta_{0dc}^{pw} pea_{dc} \bigg) +
			\bigg( \sum_{m=1,dc}^{M-1} \beta_{mdc}^{pw} 
				(\hat{pw}_{m-1dc} + E[pwt_{m-1d-1c}] - E[pwt_{m-1dc}]) \bigg) + \\
	&	&&	\qquad \qquad \bigg( \sum_{dc} \beta_{Mdc}^{pw} 
				(\sum_{M-1}^{M} \hat{pw}_{mdc} + E[pwt_{md-1c}] - E[pwt_{mdc}])\bigg) + \\
	& 	&&	\bigg( \sum_{t=1m=1dc}^{T-1M-1} \beta_{tmdc}^{ps} 
				(\hat{ps}_{t+1m-1dc} + E[pst_{t+1m-1d-1c}] - E[pst_{t+1m-1dc}]) \bigg) + \\	
	&	&&	\qquad \qquad \bigg( \sum_{t=1Mdc}^{T-1} \beta_{tmdc}^{ps} 
				(\sum_{M-1}^{M} (\hat{ps}_{t+1mdc} + E[pst_{t+1md-1c}] - E[pst_{t+1mdc}])) \bigg)
			\Bigg)
\end{alignedat}
\end{equation}

Subject to:
constraints in section "\nameref{state-action constraints}"
